---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.
-->

```{r development-2}
# Run all this chunk in the console directly
# Create "inst/" directory
dir.create(here::here("inst"))

# Example dataset
file.copy(system.file("nyc_squirrels_sample.csv", package = "fusen"), here::here("inst"))
# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows
datafile <- system.file("nyc_squirrels_sample.csv", package = "aurelier")
nyc_squirrels <- read.csv(datafile)

nyc_squirrels
```

## Data integrity check
```{r function-data-integrity}

#' Title
#'
#' @param dataset a dataset with column primary_fur_color that the function will check
#'
#' @return outputs message in the console to specify if the integrity check was successful 
#' @export
#'
#' @examples
check_data_integrity <- function(dataset){
  if(any(grepl("\\+", dataset[, "primary_fur_color"]))) {
    stop("primary_fur_color does not contain unique colors")
  } else {
    message("data integrity check ok")
  }
}

```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will be added in the '@examples' part of our function above in the "R/" directory
- This example will be added in the vignette created from this Rmd template
-->

## example
```{r examples}
datafile <- system.file("nyc_squirrels_sample.csv", package = "aurelier")
nyc_squirrels <- read.csv(datafile)

check_data_integrity(nyc_squirrels)
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will be added in the "tests/testthat/" directory
-->

```{r tests}
datafile <- system.file("nyc_squirrels_sample.csv", package = "aurelier")
nyc_squirrels <- read.csv(datafile)
nyc_squirrels_err <- nyc_squirrels
nyc_squirrels_err$primary_fur_color <- nyc_squirrels_err$combination_of_primary_and_highlight_color

test_that("check_data_integrity returns the righ messages", {
  
  expect_message(check_data_integrity(nyc_squirrels),
                 "data integrity check ok")
  expect_message(check_data_integrity(nyc_squirrels),
                 "primary_fur_color does not contain unique colors")

})

```






<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Autonomy")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
